Real-Time Systems

### 2013-10-02 beamer/dit-paper-presentation.tex
added stuff

@@

        Systems were generated by
        \begin{itemize}
            \item Generating O
            \item Generating T
            \item Generating D
        \end{itemize}

@@

	\begin{frame}{Initial description}
		[$t_d$, $t_d + H$] is a feasibility interval
	\end{frame}

\section{Numerical Example}
	\begin{frame}{Example}
		Table, OCDT, figure
	\end{frame}

>>>>

    % \subsection{Cyclic Idle Times}

    % \begin{frame}{Cyclic Idle Times}

    % \end{frame}

@@

        Systems were generated by
        \begin{itemize}
            \item Choosing $T_i$ in [5, 20]
            \item Choosing $O_i$ in [0, $H$]
            \item Choosing $D_i$ in [$T_i - CDF * T_i$, $T_i$]
        \end{itemize}

@@

    \subsection{Initial description}

	\begin{frame}{Initial description}
		The C-space is still accurately described by the following infinity of constraints:

        $$\dbf{t_1, t_2} \leq t_2 - t_1 \; \forall t_1 \leqslant  t_2$$

        As in the synchronous case,
        \begin{itemize}
            \item Every constraint is necessary
            \item Their conjunction is sufficient
            \item Most of them are redundant.
        \end{itemize}
        However the method used to remove redundancies will be different.
	\end{frame}

    \subsection{Removing redundancies}

    \begin{frame}{Feasibility study interval}

        The authors of \cite{leung1982complexity} have shown that for asynchronous systems, it sufficient to check the DBF test in intervals $[t_1, t_2]$ where $0 \leqslant t_1 \leqslant t_2$.

        Furthermore, by definition of the demand-bound function, it is sufficient to check only intervals where $t_1$ is an arrival and $t_2$ is a deadline.

    \begin{frame}{Using the FPDIT}

        If a FPDIT exists,

    \subsection{Example}

    \begin{frame}{Example}
		Table, OCDT, figure
	\end{frame}

\section{Feasibility gain of offset}

    \begin{frame}{Experiment}

        We want to express the feasibility gain of random offsets as the ratio

        $$\frac{V(\tau)}{V(\tau')}$$

        Where
        \begin{itemize}
            \item $\tau$ is a synchronous system
            \item $\tau'$ is $\tau$ with added offsets
            \item $V(\tau)$ is the size of the C-space of $\tau$
        \end{itemize}

    \begin{frame}{Result}

        \includegraphics[width=0.9\textwidth]{figs/sizeratio.png}

\section{Future Works}

    \begin{frame}{Future Works}

    \begin{itemize}
        \item Further ways of reducing redundancy before applying the simplex
        \item Other metrics to quantify the quality of the C-space
        \item Extension to multiprocessor scheduling
    \end{itemize}
